Title Text

### 2011-06-12 talk/iwtc11/paper.tex
started to describe some benchmarks

>>>>

The loop peeling optimization was implemented in the PyPy
framework. That means that the jit compilers generated for all
interpreters implemented within PyPy now can take advantage of
it. Benchmarks have been executed for a few different interpreters and
we see improvements in several cases. The ideal loop for this optimization
would be short numerical calculations with no failing guards and no
external calls.

\subsection{Python}
The python interpreter of the PyPy framework is a complete python
version 2.7 compatible interpreter. A set of numerical
calculations where implemented in both python and in C and their
runtimes compared. The benchmarks are
\begin{itemize}
\item {\bf sqrt}: approximates the square root of $y$ as $x_\infty$
  with $x_0=y/2$ and $x_k = \left( x_{k-1} + y/x_{k-1} \right) /
  2$. There are three different versions of this benchmark where $x_k$
  is represented with different type of objects: int's, float's and
  Fix16's. The later, Fix16, is a custom class that implements
  fixpoint arithmetic with 16 bits precision. In python there is only
  a single implementation of the benchmark that gets specialized
  depending on the class of it's input argument, $y$, while in C,
  there is three different implementations.
\item {\bf conv3}: one dimensional convolution with a kernel of fixed
  size $3$.
\item {\bf conv5}: one dimensional convolution with a kernel of fixed
  size $5$.
\item {\bf conv3x3}: two dimensional convolution with kernel of fixed
  size $3 \times 3$ using a custom class to represent two dimensional
  arrays.
\item {\bf dilate3x3}: two dimensional dilation with kernel of fixed
  size $3 \times 3$. This is similar to convolution but instead of
  summing over the elements, the maximum is taken. That places a
  external call to a max function within the loop that prevents some
  of the optimizations.
\item {\bf sobel}: an low level video processing algorithm used to
  locate edges in an image. It calculated the gradient magnitude
  using sobel derivatives. The algorithm is in python implemented
  on top of a custom image class that is specially designed for the
  problem. It ensures that there will be no failing guards, and makes
  a lot of the two dimension index calculations loop invariant. The
  intention there is twofold. It shows that the performance impact of
  having wrapper classes giving objects some application specific
  properties is negligible. This is due to the inlining performed
  during the tracing and the allocation removal of the index objects
  introduced. It also shows that it is possible to do some low level
  hand optimizations of the python code and hide those optimization
  under a nice interface without loosing performance.
\end{itemize}

\subsection{Numpy}
XXX: Fijal?

\subsection{Prolog}
XXX: Carl?
